I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-23 lipics-master/experiments.tex
update

>>>>

{\color{red} We also do a comparison of our method and the method in paper \cite{9211410}. They find a formula to choose nodes in their algorithm. We can use the same formula in our setting, and since we only have $\ReLU$ function, that formula can be simplified to: $$V(n) = (UB(n)-LB(n))\cdot W_{nm}.$$ In this formula, $m$ is the target node, and $n$ is one of source nodes in one layer before. We sort all nodes $n$ by their $V(n)$ values, and choose the nodes with largest values.}

### 2024-04-23 lipics-master/proofs.tex

{\color{red}Notice that above definitions only involve weights, and do not use bias. From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}

@@

{\color{red} As we mentioned before, this proof does not have any requirements on the bias.}

@@

		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not involve bias, and any kind of bias will not influence our theorem.}

@@

{\color{red} In all above statements and proofs, we do not use any assumption of bias, and the bias will have no influence on our discussion. }

>>>>

{\color{red}Notice that above definitions only involve weights, and do not use bias. As demonstrated by the following lemmas and proofs, our discussion is independent of bias, regardless of whether the bias values are very large or very small.}

@@

{\color{red} As we mentioned earlier, this proof does not have any requirements on the bias.}

@@

		{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not consider bias, and any kind of bias will not affect our theorem.}

@@

{\color{red} In all the statements and proofs above, we do not make any assumptions about bias, and bias will not affect our discussion. }
